### 2015-03-02 fundamentals/impl.tex
gets rid of vague tools comment

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based. In addition, a set of tools
are also provided to enrich the \gls{API} and supply a robust suite of behaviors
for the developer. Agent plug-ins utilize the generic core \gls{API} to
interact with one another.  For example, they use the resource exchange paradigm
\gls{API} for trading resources with one another.

>>>>

\gls{ABM} is inherently object-oriented because agents represent discrete,
independently acting objects.  Figure \ref{fig:framework} illustrates the
modular nature of \Cyclus archetypes.  The core of the \Cyclus simulator creates
a set of classes on which agent plug-ins are based.  Agent plug-ins utilize the
generic core \gls{API} to interact with one another.  For example, they use the
resource exchange paradigm \gls{API} for trading resources with one another.
